TUGAS POLINOMIAL CHAPTER 15

### 2021-10-12 Semester I/Pemrograman dalam Sains/Minggu VIII/pr.Rmd
15.3
done

```
programnya
```

@@

```
The roots:

>>>>

```
# SOAL 15.3

# koefisien polinomial
c = np.array([4.5,-3,6,-6.5,5,-1.5,2])
print ("Coefficient list")
print (c)

# save ke dalam csv
# memberikan nama file
f = open("15_3.csv","w+")

# menggambar dan menyimpan plot
plt.figure(figsize = (16,9))
plt.plot(x,y,'o-')
plt.xlabel('x')
plt.ylabel('y')
plt.savefig('15_3.png',dpi = 250)
```

@@

```
The roots:
[-0.3149883 -1.44360859j -0.3149883 +1.44360859j -0.23708958-0.88725007j
 -0.23708958+0.88725007j  0.92707788-0.60202496j  0.92707788+0.60202496j]
```
